An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
ready for reading pass

Finally, we also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
Using tools from property elicitation, we show an equivalence between minimum representative sets (those of minimum cardinality) and ``non-redundancy'', wherein no report is dominated by another.
We further show that, while a minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
The paper concludes with an interesting observation (Theorem~\ref{thm:poly-ie-implies-consistent}): while indirect property elicitation is generally a strictly weaker condition than consistency, the two are equivalent when restricting to the class of polyhedral surrogates.

@@

To prove Theorem \ref{thm:link-main}, that embedding implies calibration, we now show how to construct a calibrated link from an embedding.
In light of Theorem~\ref{thm:calibrated-separated}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.
See \S~\ref{app:sep-link-exists} for the proof.
\begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|$ produces a nonempty set of links, all of which are $\epsilon$-separated with respect to $L$ and $\ell$.
\end{restatable}

@@

\reviewertwo{C}
\raft{I made some wording edits here.  One general point though is to be careful when adding to the paper at this stage, since the notation was actually slightly off from what we had been doing, e.g.\ ``$0-1$ loss'' instead of ``0-1 loss''  and $\ell^{0-1}$ instead of $\ellzo$.}
\jessiet{Added a clause so te Weston-Watkins reference doesn't seem so random}
Interestingly, by choosing $k=1$, one obtains what appears to be a novel surrogate for 0-1 loss in multiclass settings,
\begin{align*}
	L^1(u)_y &= \left(\max_{m\in\{1,\ldots,n\}} 1 - \frac{1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
\end{align*}
In particular, this surrogate is consistent with respect to 0-1 loss using the canonical argmax link, while the Weston-Watkins hinge is not consistent for any link (\S~\ref{sec:winge}), despite being proposed as a surrogate for 0-1 loss.

@@

\section{Connection to \citet[Theorem 8]{ramaswamy2016convex}}
\label{app:ccdim-construction}

@@

The crux of their result, as in ours, in the construction of a link function exhibiting calibration.
This construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operations in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
Specifically, it operates on the \emph{superprediction set} $L(\reals^d) + \reals^\Y_+$, where the $+$ here is Minkowski addition.
An arbitrary element of the superprediction set is decomposed into a convex combination of elements of $L(\Sc)$, plus an element of $\reals^\Y_+$.
This convex combination is then thresholded at $1/|\Sc|$, where the link function may output $r\in\R$ if the weight on any $u\in\Sc$ with $\Gamma_u \subseteq \gamma_r$ is at least $1/|\Sc|$.
One can see that this construction does achieve separation, but does not necessarily align well with any norm in the surrogate report space.
It would be interesting to further compare the two constructions.

>>>>

Finally, we also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
Using tools from property elicitation, we show an equivalence between minimum representative sets (those of minimum cardinality) and ``non-redundancy'', wherein no report is dominated by another.
We further show that, while a minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
The paper concludes with an interesting observation (Theorem~\ref{thm:poly-ie-implies-consistent}): while indirect property elicitation is generally a strictly weaker condition than consistency, the two are equivalent when restricting to the class of polyhedral surrogates.%
\footnote{This result is also implicit in \citet[Theorem 8]{ramaswamy2016convex}; see \S~\ref{app:ccdim-construction}.}

@@

To prove Theorem \ref{thm:link-main}, that embedding implies calibration, we now show how to construct a calibrated link from an embedding.
In light of Theorem~\ref{thm:calibrated-separated}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.
See \S~\ref{app:sep-link-exists} for the proof.
We also discuss a more general construction in \S~\ref{sec:poly-ie-consistency}, and an alternate approach using results from \citet{ramaswamy2016convex} in \S~\ref{app:ccdim-construction}.\raft{Added}
\begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|$ produces a nonempty set of links, all of which are $\epsilon$-separated with respect to $L$ and $\ell$.
\end{restatable}

@@

\reviewertwo{C}
Interestingly, by choosing $k=1$, one obtains what appears to be a novel surrogate for 0-1 loss in multiclass settings,
\begin{align*}
	L^1(u)_y &= \left(\max_{m\in\{1,\ldots,n\}} 1 - \frac{1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
\end{align*}
In particular, this surrogate is consistent with respect to 0-1 loss using the canonical argmax link.
By contrast, recall that the Weston-Watkins hinge is not consistent for any link (\S~\ref{sec:winge}), despite being proposed as a surrogate for 0-1 loss.

@@

\section{Connection to Ramaswamy and Agarwal (2016)}
\label{app:ccdim-construction}

@@

The crux of their result, as in ours, in the construction of a link function exhibiting calibration.
Their construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operations in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
Specifically, it operates on the \emph{superprediction set} $L(\reals^d) + \reals^\Y_+$, where the $+$ here is Minkowski addition.
An arbitrary element of the superprediction set is decomposed into a convex combination of elements of $L(\Sc)$, plus an element of $\reals^\Y_+$.
This convex combination is then thresholded at $1/|\Sc|$, where the link function may output $r\in\R$ if the weight on any $u\in\Sc$ with $\Gamma_u \subseteq \gamma_r$ is at least $1/|\Sc|$.
One can see that this construction does achieve separation, but it is less explicitly aligned with any norm in the surrogate report space.
It would be interesting to further compare the two constructions.

### 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
ready for reading pass

  We thank the editor and reviewers for their feedback.  
  \jessie{Not sure what else to write here?}
  \raf{TODO}

>>>>

We thank the editor and reviewers for their feedback and suggestions.
We believe we have addressed all concerns, and the suggestions have greatly improved the paper.
Below we respond to questions and comments as appropriate.

In addition to these changes, we made a few others to address a surprisingly close connection to Ramaswamy and Agarwal (2016, Theorem 8) which was brought to our attention by Dhamma Kimpara, a PhD student at the University of Colorado Boulder.
After translating their definitions to ours, this result essentially states that, for surrogate losses with a finite representative set (the setting of our \S 6), a version of indirect elicitation implies calibration.
As such, they prove a slight generalization of our Theorem 31.
To do so, they provide an alternate link construction to ours.
We therefore felt it important to highlight their work, so we added a new appendix section (\S F) to describe the connection, and added several references to it in context: footnote 1, just before Theorem 17, and just before \S 7.1.
